Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2021-02-23 inst/manuscript/manuscript.Rmd
Updated manuscript, SI, figures with text and table, figure for field size and numbers, which is final part of results

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library(knitr)
library(citr)
library(dplyr)
library(activemapper)

@@

The vectorized map provides additional information on how the characteristics of croplands can vary geographically, ranging from narrow, strip-like fields in parts of AOI 15 (Figure 7's lower right inset) to more densely packed, less distinctly shaped fields in area such as AOI 5 (upper right inset in Figure 7). These characteristics can be summarized and mapped to explore how such characteristics vary geographically For example, average fields sizes were mapped at 0.005 degree resolution (Figure S12A), providing some indication of countrywide patterns. Given the over-estimation of fields sizes relative to the validation labels, particularly in several savanna-zone AOIs (2, 3, 6, 7, and 15), the mean sizes likely reflect agglomerations of contiguous smallholder fields, such as in AOI 2,and the southern portion of AOI 8 (Figure S12A). A closer approximation of individual field boundaries can be mapped using approaches such as regression kriging to model the relationship between the segmented boundaries and the hand drawn labels collected at validation points (Figure S12B), although such an approach introduces spatial artifacts.

@@

The results

>>>>

```{r setup, include=FALSE, cache=FALSE, message = FALSE}
library(knitr)
library(citr)
library(dplyr)
library(activemapper)
library(kableExtra)

@@

The vectorized map provides additional information on how the characteristics of croplands can vary geographically, ranging from narrow, strip-like fields in parts of AOI 15 (Figure \ref{fig:mainmap}'s lower right inset) to more densely packed, less distinctly shaped fields in area such as AOI 5 (upper right inset in Figure \ref{fig:mainmap}). To explore how field characteristics varied geographically, we mapped the average field size and total number of fields within each 0.05 degree tile (Figure S12). These patterns generally correspond to those seen in the cropland density map (Figure \ref{fig:mainmap}), with larger sizes and field counts generally aligning in the areas of higher field densities, although the biases inherent in both measures (Figures S10-11) complicate the interpretation of those variations. However, we can use the estimated to develop adjusted estimates of field sizes and counts for each AOI, and for Ghana as a whole (Table \ref{tab:sizentab}). The bias-adjusted estimates show that the typical field size in Ghana is 1.73 ha, ranging from 0.96 in AOI 4 to 2.82 ha in AOI 4, with fields in the forest zone AOIs (10, 11, 13, 14, 16) generally smaller than those in the northern half of the country (Table \ref{tab:sizentab}). The total number of fields was estimated to be 1,662,281 overall, or 205 fields per tile on average, ranging from 108/tile in AOI 4 to 399/tile in AOI 6.

```{r sizentab, echo=FALSE, warning=FALSE, message=FALSE}
fsizes_n_05 <- st_read(
  system.file("extdata/field_size_n_05.geojson", package = "activemapper"),
  quiet = TRUE
) %>% mutate(
  muarea = ifelse(is.na(muarea), 0, muarea),
  nflds = ifelse(is.na(nflds), 0, nflds),
  aoi = as.character(aoi)
)

# calculate bias factors for adjustment
data("segment_quality_stats")
# segment_quality_stats %>% filter(measure == "n")
biases <- segment_quality_stats %>%
  filter(Stat == "Mean" & scale == "grid") %>% 
  pivot_wider(names_from = type, values_from = value) %>% 
  mutate(biasfactor = Validation / Segmentation)
biases <- tile_key %>% group_by(aoi) %>% 
  count() %>% ungroup() %>% rename(ntiles = n) %>% 
  mutate(aoi = as.character(aoi)) %>% 
  left_join(biases, .) %>% 
  select(-scale, -Stat)

fsizes_05_adj <- biases %>% filter(measure == "area" & aoi != "All") %>% 
  select(aoi, biasfactor) %>% 
  rename(fbias = biasfactor) %>% 
  left_join(as_tibble(fsizes_n_05), .) %>% 
  mutate(muarea_adj = muarea * fbias) %>% select(-geometry) %>% 
  group_by(aoi) %>% 
  summarize(fsize = mean(muarea), fsizeadj = mean(muarea_adj))

# then field count
n_05_adj <- biases %>% filter(measure == "n" & aoi != "All") %>% 
  select(aoi, biasfactor, ntiles) %>% 
  rename(nbias = biasfactor) %>% 
  left_join(as_tibble(fsizes_n_05), .) %>% 
  mutate(nfldsadj = nflds * nbias) %>%
  group_by(aoi) %>% 
  summarize(N = sum(nflds), Nadj = sum(nfldsadj))

aoi_sizes_n <- left_join(fsizes_05_adj, n_05_adj) %>% 
  left_join(., biases %>% filter(measure == "area") %>% select(aoi, ntiles))

ghana_sizes_n <- aoi_sizes_n %>% 
  summarize(fsize = weighted.mean(fsize, ntiles), 
            fsizeadj = weighted.mean(fsizeadj, ntiles), 
            N = sum(N), Nadj = sum(Nadj), 
            ntiles = round(sum(ntiles)))

size_n_tab <- bind_rows(aoi_sizes_n, ghana_sizes_n) %>% 
  mutate(aoi = as.numeric(ifelse(is.na(aoi), 17, aoi))) %>% 
  arrange(aoi) %>% mutate(aoi = as.character(aoi)) %>% 
  mutate(aoi = ifelse(aoi == "17", "Ghana", aoi), 
         N_tile = round(N / ntiles),
         Nadj_tile = round(Nadj / ntiles)) %>% 
  select(aoi, ntiles, fsize, fsizeadj, N, N_tile, Nadj, Nadj_tile) %>% 
  mutate(
    ntiles = scales::number(
      round(ntiles), accuracy = 1, big.mark = ",", trim = FALSE
    ), 
    fsize = round(fsize, 2), fsizeadj = round(fsizeadj, 2), 
    N = scales::number(N, big.mark = ",", trim = FALSE), 
    N_tile = scales::number(N_tile, big.mark = ",", accuracy = 1, trim = FALSE), 
    Nadj = scales::number(round(Nadj), big.mark = ",", trim = FALSE),
    Nadj_tile = scales::number(
      round(Nadj_tile), accuracy = 1, big.mark = ",", trim = FALSE
    )
  ) %>% 
  rename(AOI = aoi, `N tiles` = ntiles, Size = fsize, `Size (adj)` = fsizeadj, 
         `N / tile` = N_tile, `N (adj)` = Nadj, 
         `N (adj) / tile` = Nadj_tile)
# size_n_tab %>% select(`N (adj) / tile`)

cap <- glue::glue("The average size and total number of crop fields for each ", 
                  "AOI and for Ghana overall. The original and bias-adjusted values", 
                  " for each measure are provided, as well as the total number", 
                  " of 0.05$^\\circ$ degree tiles in each AOI.")
knitr::kable(size_n_tab, format = "latex", booktabs = "T", caption = cap, 
             align = rep("r", 8)) %>% 
  kableExtra::kable_styling(latex_options = c("hold_position")) %>%
  kableExtra::column_spec(1:3, width = "0.45in") %>%
  kableExtra::column_spec(4:8, width = "0.85in")
```

@@

The results 
Bias in mean sizes likely reflect agglomerations of contiguous smallholder fields, and the difficulty of segmenting indistinct adjacent boundaries. Such as in AOI 2,and the southern portion of AOI 8 (Figure S12A).

### 2021-02-23 inst/manuscript/si.Rmd
Updated manuscript, SI, figures with text and table, figure for field size and numbers, which is final part of results

```{r setup, include=FALSE, cache=FALSE, message = FALSE}
library(knitr)
library(citr)
library(tidyverse)
library(sf)
library(activemapper)

@@

## Cropland characteristics
### Average field size

To examine average field sizes, the average area of the vectorized field boundaries intersecting each 0.005 degree cell in the mapping grid was calculated and mapped back onto the grid (Figure \ref{fig:fieldsize}A). Given the overestimation bias inherent in the vectorized boundaries relative to the hand-digitized validation labels, we also used a regression kriging approach [@henglRegressionkrigingEquationsCase2007] to these average field sizes for this bias. To do this, we used the estimated mean field sizes extracted from the map in Figure S12A to predict the average polygon size of the most accurate mapper's labels for each of the 1600 validation sites, using an ordinary least squares regression to model the relationship, after first log-transforming both variables. We then applied ordinary kriging (using an exponential model for the variogram) to the regression residuals, which we added to the surface of the predicted field sizes to create the adjusted surface, and then converted this back to units of hectares (Figure \ref{fig:fieldsize}B).

```{r fieldsizes, echo = FALSE, out.width="100%", fig.cap="Average fields sizes in Ghana at 0.005 degree resolution, as calculated from A) the vectorized field boundaries, and after B) adjustment against hand-drawn validation labels using a regression-kriging approach.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_fsizes.png')
```

>>>>

```{r setup, include=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(citr)
library(tidyverse)
library(sf)
library(activemapper)

@@

## Cropland characteristics
### Field area and number

To examine average field sizes, and the total number, the mean segment size per 0.05 degree tiles was calculated and mapped, as well as the total number of fields per tile (Figure \ref{fig:fieldsizes}).

```{r fieldsizes, echo = FALSE, out.width="100%", fig.cap="The A) average sizes of fields and B) total number of fields in each 0.05 degree tile, as calculated from the vectorized field boundaries.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_fsize_n_05.png')
```
